Two NIRCam channels are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-09-28 ms.tex
Some more minor wording changes but also corrected the order of the Case 1 and Case 2 which was still written incorrectly.

Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS).
%The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
The current time series observing templates available in APT are limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
These are the subarrays that will be available to Cycle 1 science programs and likely stay this way for continuity through the mission in order to stick to detector ``sweet spots'' that are well characterized and calibrated.
In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but there are operational costs to implementing and testing new modes in the OSS software and data handling.

@@

To construct the model atmospheres and generate a spectrum we require a thermal profile and molecular abundances. For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures. Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in the Oxygen abundance.

@@

For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
The readout mode in all cases simulated is RAPID readout (all reads saved without skips up the ramp discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD 209458 and 25 reads up the ramp for HAT-P-12b.

@@

The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the long wavelength grisms are used alone (Case~\ref{it:grAlone}) as compared to when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}).
These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.

>>>>

Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS).
%The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
The current time series observing templates available in APT are limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
These are the subarrays that will be available to Cycle 1 science programs and likely stay this way for continuity through the mission in order to stick to detector ``sweet spots'' that are well characterized and calibrated.
In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but the science benefits must be traded off with operational costs to implementing and testing new modes in the OSS software and data handling.

@@

To construct the model atmospheres and generate a spectrum we require a thermal profile and molecular abundances. For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures. Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in the Oxygen abundance.

@@

For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
The readout mode in all cases simulated is RAPID readout (all reads saved up the ramp without skips, discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD 209458 and 25 reads up the ramp for HAT-P-12b.

@@

The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to when the long wavelength grisms are used alone (Case~\ref{it:grAlone}).
These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.
